### 2017-02-01 local-capability-machine.tex
Some progress on the FTLR proof.

%make latex preview-mode work with natbib...
\usepackage[displaymath,floats,graphics,textmath,footnotes]{preview}

@@

  \item Case $\var{conf'} = \Phi'$, and additionally, one of the following

@@

    \item $\memreg[\Phi'](\pcreg) = \updatePcPerm{\memreg(\lv)}$
    \item $\memreg[\Phi'](\pcreg) = \var{newPc}$ and $\var{newPc} =
      ((\perm,\gl),\start,\addrend,\addr + 1)$
      \dominique{This is wrong: the semantics allow, for example, a move into
        the PC, after which the new pc is increased by one}
    and finally, for all $r \in (\RegName \setminus \{\pcreg\})$, one of the following

@@

    \item $\npair[n-1]{\memreg[\Phi']}\in\stdrr(W)$.
      \item Assume: $r \in \RegName\setminus\{\pcreg\}$.\\
        Suffices: $\npair[n-1]{\memreg[\Phi'](r)} \in \stdvr(W)$.\\
        By: definition of $\stdrr{\cdot}$

@@

        $\npair{\memreg}\in\stdrr(W)$ by definition of $\stdrr(\cdot)$ using
        Lemma~\ref{lem:stdvr-dc}.

@@

        Lemmas~\ref{lem:conds-load-suffice} and~\ref{lem:stdvr-dc} using the
        fact that $\heapSat[\memheap]{n}{W}$ and $\npair{\memreg(r_2)}\in\stdvr(W)$

@@

    \item $\npair[n-1]{\memreg[\Phi'](\pcreg)} \in \stder(W)$: TODO

>>>>

% %make latex preview-mode work with natbib...
% \usepackage[displaymath,floats,graphics,textmath,footnotes]{preview}

@@

  \item Case $\var{conf'} = \updateReg[\Phi']{\pcreg}{\var{newPc}}$, and additionally, one of the following

@@

    \item $\var{newPc}= \updatePcPerm{\memreg(\lv)}$
    \item $\var{newPc} = ((\perm',\gl'),\start',\addrend',\addr' + 1)$ and
      $\memreg[\Phi'](\pcreg) = ((\perm',\gl'),\start',\addrend',\addr')$
    and finally, for all $r \in \RegName$, one of the following

@@

    \item For all $r \in \RegName$, $\npair[n-1]{\memreg[\Phi'](r)}\in\stdvr(W)$.

@@

        Step~\ref{step:ftlr-reg-rr} using Lemma~\ref{lem:stdvr-dc}.

@@

        Lemmas~\ref{lem:conds-load-suffice} using the fact that
        $\heapSat[\memheap]{n}{W}$ and $\npair{\memreg(r_2)}\in\stdvr(W)$ which
        we have from step~\ref{step:ftlr-reg-rr}.

@@

    \item $\npair[n-1]{\memreg[\Phi']}\in\stdrr(W)$: Follows from the previous
      point by definition of $\stdrr(W)$.
    \item $\npair[n-1]{\var{newPc}} \in \stder(W)$:
      \item Case $\var{newPc}= \updatePcPerm{\memreg(\lv)}$: We distinguish the
        following cases:
        \item Case $\memreg(\lv) = ((\entry,\gl'),\start',\addrend',\addr')$:
          \item $\npair[n-1]{\memreg(\lv)} \in \stdvr(W)$.  Follows from
            Step~\ref{step:ftlr-reg-rr} using Lemma~\ref{lem:stdvr-dc}.
          \item $\npair[n-1]{(\start',\addrend',addr') \in
              \entryCond{\gl'}(W)}$. By definition of $\stdvr(W)$ from the
            previous point.
          \item 
      \item Case $\var{newPc} = ((\perm',\gl'),\start',\addrend',\addr' + 1)$ and
        $\memreg[\Phi'](\pcreg) = ((\perm',\gl'),\start',\addrend',\addr')$: TODO
